A Test of the Frequency Independence Assumption of the Power System Parameters used in Geomagnetically Induced Current Calculations

### 2019-02-01 paper.tex
Updates from ShareLaTeX

The primary conclusions of this work follow from the results shown in Table~1: the frequency dependent model, Model 2, is significantly better at predicting $GIC$ than the frequency independent model, Model 1. Model 3, which uses magnetic field measurements as in input provides better estimates of $GIC$ than Model 2. Model 4, in which a transfer function that connects $GIC$ to $\mathbf{B}$ was derived directly from the data, provides the best predictions of $GIC$.

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_predictions-MeanModel-20060806T150000.pdf}
\caption{Out-of-sample model predictions and predictions errors for a 1-day interval. The bottom overlapping traces are the measured GIC (black line) and the model predictions (colored lines). The prediction error of each model is shown shifted by an arbitrary offset.}
\label{predictions}
\end{figure}

>>>>

The primary conclusions of this work follow from the results shown in Table~1: the frequency dependent model, Model 2, is significantly better at predicting GIC than the frequency independent model, Model 1. Model 3, which uses magnetic field measurements as in input provides better estimates of $GIC$ than Model 2. Model 4, in which a transfer function that connects $GIC$ to $\mathbf{B}$ was derived directly from the data, provides the best predictions of $GIC$.

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_predictions-MeanModel-20060806T150000.pdf}
\caption{Out-of-sample model predictions (top) and predictions errors for a 1-day interval. Note that the scales for Models 2-4 differ from that for Model 1.}
\label{predictions}
\end{figure}
